On the error performance of the $A_n$ lattices

### 2011-11-02 paper.tex
removed hard newlines.

%\documentclass[a4paper,10pt]{article}
\documentclass[draftcls, onecolumn, 11pt]{IEEEtran}
%\documentclass[journal]{../bib/IEEEtran}
%\documentclass[correspondence,9pt]{../bib/IEEEtran}

@@

The Voronoi cell is linked with the problem of \emph{lattice
decoding}.  Given some point $\ybf \in \reals^n$ a \emph{lattice
decoder} (or \emph{nearest lattice point algorithm}) returns the
lattice point in $\Lambda$ that is nearest to
$\ybf$~\cite{Agrell2002}.  Equivalently it returns the lattice point
$\xbf$ such that the translated Voronoi cell $\vor(\Lambda) + \xbf$
contains $\ybf$.  Computationally lattice decoding is known to be
NP-hard under certain conditions when the lattice itself, or rather a
basis thereof, is considered as an additional input
parameter~\cite{micciancio_hardness_2001,
Jalden2005_sphere_decoding_complexity}. Nevertheless, algorithms exist
that can compute the nearest lattice point in reasonable time if the
dimension is small (approximately $n \leq 60$). One such algorithm is
the \term{sphere decoder}~\cite{Viterbo_sphere_decoder_1999,Pohst_sphere_decoder_1981,Agrell2002}.
 %Kannan~\cite{Kannan1987_fast_general_np} suggested a different approach that is known to be asymptotically faster than the sphere decoder. 
A good overview of these techniques is given by~\cite{Agrell2002}.
Fast nearest point algorithms are known for specific
lattices~\cite{Conway1982FastQuantDec, McKilliam2008,
McKilliam2009CoxeterLattices,Vardy1993_leech_lattice_MLD}. For
example, the root lattices $D_n$ and $A_n$ and their dual lattices
$D_n^*$ and $A_n^*$ can be decoded in linear-time, i.e. in a number of
operations of order $O(n)$~\cite{Conway1982FastQuantDec,McKilliam2009CoxeterLattices}.

>>>>

%\documentclass[a4paper,10pt]{article}
\documentclass[draftcls, onecolumn, 11pt]{IEEEtran}
%\documentclass[journal]{IEEEtran}
%\documentclass[correspondence,9pt]{../bib/IEEEtran}

@@

The Voronoi cell is linked with the problem of \emph{lattice decoding}.  Given some point $\ybf \in \reals^n$ a \emph{lattice decoder} (or \emph{nearest lattice point algorithm}) returns the lattice point in $\Lambda$ that is nearest to $\ybf$~\cite{Agrell2002}.  Equivalently it returns the lattice point $\xbf$ such that the translated Voronoi cell $\vor(\Lambda) + \xbf$ contains $\ybf$.  Computationally lattice decoding is known to be NP-hard under certain conditions when the lattice itself, or rather a basis thereof, is considered as an additional input parameter~\cite{micciancio_hardness_2001, Jalden2005_sphere_decoding_complexity}. Nevertheless, algorithms exist that can compute the nearest lattice point in reasonable time if the dimension is small (approximately $n \leq 60$). One such algorithm is the \term{sphere decoder}~\cite{Viterbo_sphere_decoder_1999,Pohst_sphere_decoder_1981,Agrell2002}.
 %Kannan~\cite{Kannan1987_fast_general_np} suggested a different approach that is known to be asymptotically faster than the sphere decoder. 
A good overview of these techniques is given by~\cite{Agrell2002}. Fast nearest point algorithms are known for specific lattices~\cite{Conway1982FastQuantDec, McKilliam2008,McKilliam2009CoxeterLattices,Vardy1993_leech_lattice_MLD}. For example, the root lattices $D_n$ and $A_n$ and their dual lattices $D_n^*$ and $A_n^*$ can be decoded in linear-time, i.e. in a number of operations of order $O(n)$~\cite{Conway1982FastQuantDec,McKilliam2009CoxeterLattices}.
